Confirmation of \srcfull{} as a long period radio transient

### 2025-05-23 paper/main.tex
Added peak flux to the table of pulse properties, and added table to appendix

We also re-imaged the original 2023-05-28 L-band MeerKAT observation described in \citetalias{2024MNRAS.535..909D}, which was taken under project code DDT-20230525-DD-01 under capture block 1685306788. We performed a similar processing of the data, and identified four pulses with ToAs consistent with an ephemeris derived from the other data. The folded and stacked dynamic spectra are shown in \Fig~\ref{fig:stacked_spectra}.

@@

%\begin{deluxetable*}{ccccc}
%  \tablecaption{Times of arrival and pulse properties\label{tbl:toas}}
%  \tablehead{
%    \colhead{Telescope} & \colhead{$\nu$} & \colhead{ToA} & \colhead{Fluence} & \colhead{$\sigma$} \\ 
%    & \colhead{(MHz)} & \colhead{(MJD)} & \colhead{(Jy\,s)} & \colhead{(s)}
%  } 
%  \startdata
%ASKAP & 888 & 59965.0429346(42) & 13.4(2) & 29.1(4) \\
%MWA & 170 & 59966.061584(40) & 358(55) & 40(7) \\
%ASKAP & 888 & 60040.913447(32) & 1.0(1) & 25(3) \\
%MeerKAT & 1284 & 60092.8995476(100) & 0.104(7) & 12.8(9) \\
%MeerKAT & 1284 & 60092.947966(10) & 0.10(1) & 12(1) \\
%MeerKAT & 1284 & 60092.996466(11) & 0.125(7) & 15.8(9) \\
%MeerKAT & 1284 & 60093.044919(12) & 0.122(7) & 16(1) \\
%MWA & 200 & 60481.637466(65) & 50(11) & 24(8) \\
%MWA & 200 & 60485.658977(33) & 29(3) & 16(4) \\
%MWA & 200 & 60489.632266(20) & 48(3) & 14(2) \\
%MWA & 200 & 60492.588020(24) & 87(7) & 14(3) \\
%MWA & 200 & 60496.609639(18) & 67(4) & 17(2) \\
%MWA & 200 & 60503.587085(14) & 82(3) & 17(2) \\
%ASKAP & 888 & 60503.6347610(51) & 6.2(2) & 16.4(5) \\
%MWA & 200 & 60506.542809(33) & 57(7) & 9(4) \\
%MWA & 200 & 60510.564531(11) & 79(3) & 16(1) \\
%MWA & 200 & 60519.528812(29) & 86(10) & 14(4) \\
%MWA & 200 & 60522.533028(16) & 76(3) & 18(2) \\
%MWA & 200 & 60527.524033(14) & 73(3) & 16(2) \\
%MWA & 200 & 60530.528339(16) & 68(4) & 17(2) \\
%MWA & 200 & 60537.506042(13) & 92(4) & 17(2) \\
%MWA & 200 & 60541.479448(47) & 41(6) & 14(5) \\
%MWA & 200 & 60544.483761(15) & 79(3) & 20(2) \\
%MWA & 200 & 60551.461625(16) & 85(4) & 16(2) \\
%MWA & 185 & 60572.395455(15) & 74(3) & 15(2) \\
%MWA & 185 & 60572.443943(21) & 73(4) & 16(2) \\
%MWA & 185 & 60572.540824(18) & 64(4) & 16(2) \\
%MWA & 185 & 60572.589281(31) & 82(8) & 21(4) \\
%MWA & 200 & 60592.456765(27) & 34(3) & 19(3) \\
%MWA & 200 & 60592.505159(33) & 35(4) & 19(4) \\
%MWA & 200 & 60593.474369(26) & 29(3) & 15(3) \\
%MWA & 200 & 60593.522901(46) & 27(4) & 19(5) \\
%MWA & 200 & 60594.443484(21) & 43(3) & 18(2) \\
%MWA & 200 & 60594.491990(33) & 19(2) & 12(4) \\
%MWA & 200 & 60595.461118(29) & 33(3) & 19(3) \\
%MWA & 200 & 60595.509617(25) & 27(2) & 13(3) \\
%MWA & 200 & 60596.430283(20) & 39(3) & 16(2) \\
%MWA & 200 & 60596.478721(23) & 39(3) & 17(3) \\
%MWA & 200 & 60597.447846(41) & 22(3) & 16(5) \\
%MWA & 200 & 60597.496319(30) & 38(4) & 19(3) \\
%MWA & 200 & 60599.434635(17) & 39(2) & 13(2) \\
%MWA & 200 & 60599.483122(24) & 32(3) & 13(3) \\
%MWA & 200 & 60600.500655(31) & 30(3) & 16(4) \\
%MWA & 200 & 60602.438964(32) & 36(4) & 21(4) \\
%MWA & 200 & 60602.487394(27) & 39(3) & 20(3) \\
%MeerKAT & 813 & 60602.5835733(40) & 1.64(4) & 14.9(4) \\
  %\enddata
%\end{deluxetable*}

These ToAs were then barycentred and fit for both period and DM, resulting in the values given in \Tab~\ref{tbl:ephemeris}.
The residuals are plotted in \ref{fig:pulse_details}, along with the fitted pulse widths and fluences.
We also tried fitting a timing model that included a spin-down parameter, and found that it was consistent with zero spin-down to within $1\sigma$, and so is not included in the ephemeris.

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.98\linewidth]{pulse_details.pdf}
  \caption{Timing residuals (top panel) and other pulse properties derived from the fits of \Eqn~\ref{eqn:emg} to the individual light curves (second and third panels). The peak flux, $S_{\rm peak}$, equivalent to the $A$ parameter in \eqn~\ref{eqn:emg}, is the peak flux of the modelled unscattered pulse. The bottom panel displays $S_{\rm peak,1 GHz} = S_{\rm peak} (\nu/{\rm GHz})^{-\alpha}$, where $\alpha = -2$ has been assumed. Notable features of interest include the relative brightness of the early 2023 detections (leftmost two points), and the relative stability of the pulse fluences (and pulse morphology) of the MWA detections in the time range $60480 \le {\rm MJD} \le 60580$.}
  \label{fig:pulse_details}
\end{figure*}

@@

>>>>

We also re-imaged the original 2023-05-28 L-band MeerKAT observation described in \citetalias{2024MNRAS.535..909D}, which was taken under project code DDT-20230525-DD-01 under capture block 1685306788. We performed a similar processing of the data, and identified four pulses with ToAs consistent with an ephemeris derived from the other data. The folded and stacked dynamic spectra are shown in \Fig~\ref{fig:stacked_spectra}\footnote{The signal-to-noise of the MeerKAT detections was insufficient to improve on the localisation derived in \citetalias{2024MNRAS.535..909D}.}.

@@

These ToAs were then barycentred and fit for both period and DM, resulting in the values given in \Tab~\ref{tbl:ephemeris}.
The residuals are presented in \Fig~\ref{fig:pulse_details} and \Tab~\ref{tbl:toas}, along with other fitted properties of the pulses.
We also tried fitting a timing model that included a spin-down parameter, and found that it was consistent with zero spin-down to within $1\sigma$, and so is not included in the ephemeris.

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.98\linewidth]{pulse_details.pdf}
  \caption{Timing residuals (top panel) and other pulse properties derived from the fits of \Eqn~\ref{eqn:emg} to the individual light curves (second and third panels). The peak flux, $S_{\rm peak}$, equivalent to the $A$ parameter in \eqn~\ref{eqn:emg}, is the peak flux of the modelled unscattered pulse. The bottom panel displays $S_{\rm peak,1 GHz} = S_{\rm peak} (\nu/{\rm GHz})^{-\alpha}$, where $\alpha = -2$ has been assumed. Notable features of interest include the relative brightness of the early 2023 detections (leftmost two points), and the relative stability of the pulse fluences (and pulse morphology) of the MWA detections in the time range $60480 \le {\rm MJD} \le 60580$. See \Tab~\ref{tbl:toas} for the values shown in this figure.}
  \label{fig:pulse_details}
\end{figure*}

@@

\section{Pulse properties}

\Tab~\ref{tbl:toas} provides the fitted parameter values of the pulses shown in \Fig~\ref{fig:pulse_details}.

\begin{table*}
  \centering
  \caption{Times of arrival and other fitted pulse properties}
  \label{tbl:toas}
  \begin{tabular}{cccccc}
\hline
Telescope & Freq & ToA & $S_{\rm peak}$ & $\sigma$ & Fluence \\
 & (MHz) & (MJD) & (Jy) & (s) & (Jy\,s) \\
\hline
ASKAP & 888 & 59965.0429346(42) & 0.184(5) & 29.1(4) & 13.4(2) \\
MWA & 170 & 59966.061584(40) & 4(1) & 40(7) & 358(55) \\
ASKAP & 888 & 60040.913447(32) & 0.015(3) & 25(3) & 1.0(1) \\
MeerKAT & 1284 & 60092.8995476(100) & 0.0032(4) & 12.8(9) & 0.104(7) \\
MeerKAT & 1284 & 60092.947966(10) & 0.0033(6) & 12(1) & 0.10(1) \\
MeerKAT & 1284 & 60092.996466(11) & 0.0032(3) & 15.8(9) & 0.125(7) \\
MeerKAT & 1284 & 60093.044919(12) & 0.0030(3) & 16(1) & 0.122(7) \\
MWA & 200 & 60481.637466(65) & 0.8(4) & 24(8) & 50(11) \\
MWA & 200 & 60485.658977(33) & 0.7(2) & 16(4) & 29(3) \\
MWA & 200 & 60489.632266(20) & 1.4(3) & 14(2) & 48(3) \\
MWA & 200 & 60492.588020(24) & 2.4(6) & 14(3) & 87(7) \\
MWA & 200 & 60496.609639(18) & 1.5(3) & 17(2) & 67(4) \\
MWA & 200 & 60503.587085(14) & 2.0(2) & 17(2) & 82(3) \\
ASKAP & 888 & 60503.6347610(51) & 0.151(7) & 16.4(5) & 6.2(2) \\
MWA & 200 & 60506.542809(33) & 2(1) & 9(4) & 57(7) \\
MWA & 200 & 60510.564531(11) & 2.0(2) & 16(1) & 79(3) \\
MWA & 200 & 60519.528813(29) & 2.4(8) & 14(4) & 86(10) \\
MWA & 200 & 60522.533028(16) & 1.6(2) & 18(2) & 76(3) \\
MWA & 200 & 60527.524033(14) & 1.8(2) & 16(2) & 73(3) \\
MWA & 200 & 60530.528339(16) & 1.6(2) & 17(2) & 68(4) \\
MWA & 200 & 60537.506042(13) & 2.1(3) & 17(2) & 92(4) \\
MWA & 200 & 60541.479447(47) & 1.1(5) & 14(5) & 41(6) \\
MWA & 200 & 60544.483761(15) & 1.6(2) & 20(2) & 79(3) \\
MWA & 200 & 60551.461625(16) & 2.2(3) & 16(2) & 85(4) \\
MWA & 185 & 60572.395455(15) & 1.9(3) & 15(2) & 74(3) \\
MWA & 185 & 60572.443943(21) & 1.8(3) & 16(2) & 73(4) \\
MWA & 185 & 60572.540824(18) & 1.6(3) & 16(2) & 64(4) \\
MWA & 185 & 60572.589281(31) & 1.6(4) & 21(4) & 82(8) \\
MWA & 200 & 60592.456765(27) & 0.7(2) & 19(3) & 34(3) \\
MWA & 200 & 60592.505159(33) & 0.7(2) & 19(4) & 35(4) \\
MWA & 200 & 60593.474369(26) & 0.8(2) & 15(3) & 29(3) \\
MWA & 200 & 60593.522901(46) & 0.6(2) & 19(5) & 27(4) \\
MWA & 200 & 60594.443484(21) & 0.9(2) & 18(2) & 43(3) \\
MWA & 200 & 60594.491990(33) & 0.6(3) & 12(4) & 19(2) \\
MWA & 200 & 60595.461118(29) & 0.7(2) & 19(3) & 33(3) \\
MWA & 200 & 60595.509617(25) & 0.8(2) & 13(3) & 27(2) \\
MWA & 200 & 60596.430283(20) & 1.0(2) & 16(2) & 39(3) \\
MWA & 200 & 60596.478721(23) & 0.9(2) & 17(3) & 39(3) \\
MWA & 200 & 60597.447846(41) & 0.5(2) & 16(5) & 22(3) \\
MWA & 200 & 60597.496319(30) & 0.8(2) & 19(3) & 38(4) \\
MWA & 200 & 60599.434635(17) & 1.2(2) & 13(2) & 39(2) \\
MWA & 200 & 60599.483122(24) & 1.0(3) & 13(3) & 32(3) \\
MWA & 200 & 60600.500655(31) & 0.7(2) & 16(4) & 30(3) \\
MWA & 200 & 60602.438964(32) & 0.7(2) & 21(4) & 36(4) \\
MWA & 200 & 60602.487394(27) & 0.8(2) & 20(3) & 39(3) \\
MeerKAT & 813 & 60602.5835733(40) & 0.044(2) & 14.9(4) & 1.64(4) \\
\hline
  \end{tabular}
\end{table*}
